Mapping malaria by sharing spatial information between incidence and prevalence datasets

### 2019-12-06 si.tex
Update si authors.

% Title must be 250 characters or less.
\begin{flushleft}
{\Large
\textbf\newline{Supplementary Material: Joint modelling of aggregated incidence data and point prevalence surveys for malaria mapping} % Please use "sentence case" for title and headings (capitalize only the first word in a title (or heading), the first word in a subtitle (or subheading), and any proper nouns).
}
\newline
% Insert author names, affiliations and corresponding author email (do not include titles, positions, or degrees).
\\
Tim C.D. Lucas*\textsuperscript{1}, Anita Nandi\textsuperscript{1}, Michele Nguyen\textsuperscript{1}, Susan Rumisha \textsuperscript{1}, Rosalind Howes \textsuperscript{1}, Katherine E. Battle \textsuperscript{1}, Andre Python \textsuperscript{1}, Ewan Cameron\textsuperscript{1}, Pete Gething\textsuperscript{1} and Daniel J. Weiss\textsuperscript{1}
\\
\bigskip
\textbf{1} BDI, Oxford
\\
\bigskip

>>>>

% Title must be 250 characters or less.
\begin{flushleft}
{\Large
\textbf\newline{Supplementary Material: Joint modelling of aggregated incidence data and point prevalence surveys for malaria mapping} % Please use "sentence case" for title and headings (capitalize only the first word in a title (or heading), the first word in a subtitle (or subheading), and any proper nouns).
}
\newline
% Insert author names, affiliations and corresponding author email (do not include titles, positions, or degrees).
\\
Tim C.D. Lucas*\textsuperscript{1}, 
Anita K. Nandi\textsuperscript{1},
Elisabeth G. Chestnutt\textsuperscript{1},
Katherine A. Twohig\textsuperscript{1},
Suzanne H. Keddie\textsuperscript{1},
Emma L. Collins\textsuperscript{1},
Rosalind E. Howes\textsuperscript{1},
Michele Nguyen\textsuperscript{1},
Susan F. Rumisha\textsuperscript{1},
Andre Python\textsuperscript{1},
Rohan Arambepola\textsuperscript{1},
Amelia Bertozzi-Villa\textsuperscript{1,2},
Penelope Hancock\textsuperscript{1},
Punam Amratia\textsuperscript{1},
Katherine E. Battle\textsuperscript{1},
Ewan Cameron\textsuperscript{1},
Peter W. Gething\textsuperscript{1, 3, 4}
Daniel J. Weiss\textsuperscript{1}
\\
\bigskip
1. BDI, Oxford\\
2. Institute for Disease Modeling, Bellevue, WA, USA\\
3. Telethon Kids Institute, Perth Children’s Hospital, Perth, Australia\\
4. Curtin University, Perth, Australia
\\
\bigskip
